module2IVgraphs

### 2022-04-11 module2/module2IVgraphs.Rmd
figuring out graphs for eco-pol variables

ggplot(govtgraph, aes(x = technology, y= mean, group = Govt))+
  geom_line(aes(colour = Govt, line = Govt)) 
  #ylim(0,4)
  #scale_color_manual(values = c("darkred", "steelblue"))

@@

ecopolscalescores <- codedmodule2 %>%
  select(starts_with(c("Risky","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  dplyr::mutate(Pro_decentralisation = mean(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
   dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
   dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
   dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
  dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")) %>%
    na.omit()

ggplot(ecopolscalescores, aes(Pro_decentralisation, Risky_Hydro))+
  geom_point()

@@

>>>>

p <- ggplot(govtgraph, aes(x = technology, y= mean, group = Govt))+
  geom_line(aes(colour = Govt, line = Govt)) +
  labs(y = "mean perceived risk", x = "energy technology")

update_labels(p, list(colour = "Preferred Government Type"))
  #ylim(0,4)
  #scale_color_manual(values = c("darkred", "steelblue"))

@@

demorisk2 <- codedmodule2%>%
  group_by(SYSTEMDEMO)%>%
  filter(SYSTEMDEMO %in% c(1, 5))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(SYSTEMDEMO, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)

demorisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = SYSTEMDEMO))+
  geom_line(aes(colour = SYSTEMDEMO, line = SYSTEMDEMO))

@@

decenrisk2 <- codedmodule2%>%
    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  dplyr::mutate(Pro_decentralisation = sum(c_across("DECISIONDECEN":"DECISIONCEN"))) %>%
  group_by(Pro_decentralisation)%>%
  filter(Pro_decentralisation %in% c(2, 10))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(Pro_decentralisation, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)

decenrisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = Pro_decentralisation))+
  geom_line(aes(colour = Pro_decentralisation, line = Pro_decentralisation))+
  ylim(1,4)
```

largerisk2 <- codedmodule2%>%
    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  dplyr::mutate(Pro_largescale = sum(c_across("INDUSTRYLARGE":"INDUSTRYSMALL"))) %>%
  group_by(Pro_largescale)%>%
  filter(Pro_largescale%in% c(2, 10))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(Pro_largescale, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)

largerisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = Pro_largescale))+
  geom_line(aes(colour = Pro_largescale, line = Pro_largescale))+
  ylim(1,4)
```

globalrisk2 <- codedmodule2%>%
    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  dplyr::mutate(Pro_global = sum(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL"))) %>%
  group_by(Pro_global)%>%
  filter(Pro_global%in% c(2, 10))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(Pro_global, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)

globalrisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = Pro_global))+
  geom_line(aes(colour = Pro_global, line = Pro_global))+
  ylim(1,4)
```

envrisk2 <- codedmodule2%>%
    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  group_by(ENVOVERDEV)%>%
  filter(ENVOVERDEV%in% c(1, 5))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(ENVOVERDEV, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)

envrisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = ENVOVERDEV))+
  geom_line(aes(colour = ENVOVERDEV, line = ENVOVERDEV))+
  ylim(1,4)
```

devrisk2 <- codedmodule2%>%
    select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  group_by(DEVOVERENV)%>%
  filter(DEVOVERENV%in% c(1, 5))%>%
  summarize_at(vars(starts_with(c("RISKY"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_Hydro_mean, Risky_Solar_mean, Risky_Wind_mean, Risky_Nuclear_mean, Risky_Coal_mean, Risky_Gas_mean, Risky_Oil_mean, Risky_Hydro_sd, Risky_Solar_sd, Risky_Wind_sd, Risky_Nuclear_sd, Risky_Coal_sd, Risky_Gas_sd, Risky_Oil_sd) %>%
  select(DEVOVERENV, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean)

devrisk2 %>%
  group_by(technology) %>%
  ggplot(aes(x = technology, y= mean, group = DEVOVERENV))+
  geom_line(aes(colour = DEVOVERENV, line = DEVOVERENV))+
  ylim(1,4)
```

ecopolscalescores <- codedmodule2 %>%
  select(starts_with(c("Risky","Ben","SYSTEMDEMO","SYSTEMRELIGION","SYSTEMTECHNO","SYSTEMTOTAL","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")))%>%
  rowwise()%>%
  dplyr::mutate(Pro_decentralisation = sum(c_across("DECISIONDECEN":"DECISIONCEN")))%>%
   dplyr::mutate(Pro_largescale = mean(c_across("INDUSTRYLARGE":"INDUSTRYSMALL")))%>%
   dplyr::mutate(Pro_global = mean(c_across("ECONOMYGLOBAL":"ECONOMYLOCAL")))%>%
   dplyr::mutate(Pro_ecogrowth = mean(c_across("ENVOVERDEV":"DEVOVERENV")))%>%
   dplyr::mutate(Pro_private = mean(c_across("OWNERPVT":"OWNERREG")))%>%
  #dplyr::select(!c("DECISIONDECEN","DECISIONCEN", "INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL", "ECONOMYLOCAL","ENVOVERDEV",     "DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG")) %>%
    na.omit()

ggplot(ecopolscalescores, aes(Pro_decentralisation, Ben_Nuclear))+
  geom_count()
